Kindly Bent to Free Us

### 2020-03-04 kindly/extensions.tex
linear lists
Small additions.

@@

Patterns like this one are dynamically safe because $a$ is not used after
the second line.
Non-lexical lifetimes handle such patterns by removing expressions
that do not mention $a$ from its region; in this example,  the
expression on the last line.
%
In \lang, regions are purely lexical and marked by the
expression $\region{b}{e}$.
During inference, region typing is only done when exiting the region:
we modify the usage environment and introduce a kind constraint to prevent
escaping.

We can thus replace the lexical region by
an annotation on each subexpression indicating which borrowing it is associated
to. When exploring a subexpression, we compare the annotations, and automatically
apply the $\textsc{Region}$ rule when they differ.
%
This approach is equivalent to inlining the $\textsc{Region}$ rule in all the other
rules.

>>>>

\subsection{Branching constructs}

Our formalization of \lang does not contain branching constructs. As a consequence,
subexpressions are always executed sequentially. This is of great importance
for the splitting relation introduced in \cref{sdtyping}, as it must
coincide with the order of evaluation. To account for borrows and linear
values in different branches, we need a new (symmetric) join relation.
This relation immediately follows from the semantics of borrows and linearity
shown so far, and allow to easily define branching constructs such as if-then-else
and pattern matching.
This extension is implemented in our prototype.

@@

Such code patterns are dynamically safe since $a$ is not used after
the second line.
Non-lexical lifetimes handle this by removing expressions
that do not mention $a$ from its region; in this example,  the
expression on the last line.
%
In \lang, regions are purely lexical and marked by the
expression $\region{b}{e}$.
During inference, we introduce kind constraint to prevent escaping from
a region.

We can replace the lexical region by
an annotation on each expression indicating which borrows are live
in this expression.
When exploring a subexpression, we compare the annotations, and automatically
apply the $\textsc{Region}$ rule when they differ.
%
This approach is equivalent to inlining the $\textsc{Region}$ rule in all the other
rules.
